Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-11 write-ups/PLDI/paper.tex
Related work sketch.

@@

\ADComment{Mention dynamic parallelism and explain why it's no good.}

>>>>

Lots of work on irregular algorithms (assumes fairness), and persistent threads (assumes OB model, which assumes a degree of fairness).  Our contribution can enable these to be safe.

Work on multi-tasking to improve throughput, etc., but this does not relate to fairness and wouldn't help blocking algorithms.

Proposals to implement preemption, but these require hardware support and may be overkill.  Advantage: fully automatic; disadvantage: doesn't capture domain knowledge.

Dynamic parallelism could be extended to give barriers, but doesn't work with work stealing (less general).  It is in recent OpenCL.

@@
